\feelchapter{Getting Started with Feel++}
            {Getting Started with Feel++}
            {Christophe Prud'homme, Baptiste Morin, Guillaume Dollé}
            {getting-started}


% first application
\input{tutorial/myapp}


\subsection{Initializing PETSc and Trilinos}

\index{PETSc}\index{Trilinos}\index{Libraries!PETSc}\index{Libraries!Trilinos}

PETSc is a suite of data structures and routines for the scalable (parallel)
solution of scientific applications modeled by partial differential
equations. It employs the MPI standard for parallelism.

\feel supports the PETSc framework, the \lstinline!Environment! \index{Environment}
takes care of initializing the associated PETSc environment.


% mesh manipulation
\input{tutorial/mymesh}

% integrals computing
\input{tutorial/myintegrals}

% function spaces
\input{tutorial/myfunctionspace}

% solve laplacian dirichlet homogene
\input{tutorial/mylaplacian}

% solve stokes poiseuille flow
\input{tutorial/mystokes}

% solve advection equations
\input{tutorial/myadvection}

\section{Linear Algebra}
\label{sec:linear-algebra}

\feel supports \textsc{PETSc} as it Linear algebra backend. \textsc{PETSc} is a
suite of data structures and routines for the scalable solution of scientific
applications modeled by PDE available at
\url{http://www.mcs.anl.gov/petsc/petsc-as/}



\subsection{Choosing a linear algebra backend}
\label{sec:choos-line-algebra}

\index{Class!Backend}\index{boost!shared\_ptr}
To select a backend in order to solve a linear system, we instantiate
the \lstinline!Backend! class associated :
\begin{lstlisting}
#include <feel/feelalg/backend.hpp>
boost::shared_ptr<Backend<double> > backend =
     Backend<double>::build( BACKEND_PETSC );
\end{lstlisting}
The backend provides an interface to solve
\begin{equation}
  \label{eq:8}
  A x = b
\end{equation}
where $A$ is a $n \times n $ sparse matrix and $x,b$ vectors of size $n$. The backend defines the \cpp types for  each of these, e.g :
\begin{lstlisting}
Backend<double>::sparse_matrix_type A;
Backend<double>::vector_type x,b;
\end{lstlisting}
In practice, we use the \lstinline!boost::shared_ptr<>! shared pointer
to ensure that we won't get memory leaks. The backends provide a
corresponding \lstinline!typedef!

\begin{lstlisting}
Backend<double>::sparse_matrix_ptrtype A( backend->newMatrix( Xh, Yh ) );
Backend<double>::vector_ptrtype x( backend->newVector( Yh ) );
Backend<double>::vector_ptrtype b( backend->newVector( Xh ) );
\end{lstlisting}
where $X_h$ and $Y_h$ are function spaces providing the number of
degrees of freedom that will define the size of the matrix and vectors
thanks to the helpers functions \lstinline!Backend::newMatrix()! and
\lstinline!Backend::newVector!. In a parallel setting, the
local/global processor mapping would be passed down by the function
spaces.

%\subsection{Defining and using matrices and vectors}
%\label{sec:defin-using-matr}

\subsection{Solving}
\label{sec:solving}

To solve the linear problem $Ax=b$, the backend provides a function \lstinline!solve! with three required parameters
\begin{lstlisting}
 solve(_matrix=A, _solution=x, _rhs=b)
\end{lstlisting}
where :
\begin{itemize}
\item the matrix $A$ has a \lstinline!sparse_matrix_ptrtype! type
\item the solution $x$ has a type \lstinline!vector_type! or \lstinline!vector_ptrtype!
\item the second member vector $b$ has a type \lstinline!vector_ptrtype!
\end{itemize}
You can also add optional parameters like :
\begin{itemize}

\item a preconditioner : instead of solving $Ax=b$, we solve $P^{-1}Ax= P^{-1}b$. This method can be applied in iterative methods and permits to decrease the number of iterations in the resolution system

\item a maximum number of iterations : this option is used with an iterative solving method

\item a residual tolerance : the fraction $\displaystyle{\frac{\mid\mid r^{(k)} \mid\mid }{\mid\mid r^{(0)} \mid\mid}}$ is inferior to the residual tolerance with
$r^{(k)}=b-Ax^{(k)}$ and $x^{(k)}$ the solution at the $k^{th}$ iteration

\item a absolute tolerance : $\mid\mid r^{(k)} \mid\mid $ is inferior to the absolute tolerance

\item a different tolerance : sometimes, the residue doesn’t decrease continuously during the iterations. The difference between two plots doesn’t have to exceed the parameter choosen for the difference tolerance.

\item a boolean to use transpose matrix : instead of solving $Ax=b$, we solve $A^{t}x=b$. If $A$ is defined and positive, $A^{t}=A$.

\end{itemize}

To have a view of the values of the optional parameters, see the following code :

\begin{lstlisting}
BOOST_PARAMETER_MEMBER_FUNCTION(
	(solve_return_type),
         solve,
         tag,
         (required
	(matrix,(sparse_matrix_ptrtype))
	(in_out(solution),*(mpl::or_<boost::is_convertible<mpl::_,vector_type&>,
                                         boost::is_convertible<mpl::_,vector_ptrtype> >))
	(rhs,(vector_ptrtype)))
	(optional
	  (prec,(sparse_matrix_ptrtype), matrix )
	  (maxit,(size_type), 1000 )
	  (rtolerance,(double), 1e-13)
	  (atolerance,(double), 1e-50)
	  (dtolerance,(double), 1e5)
	  (reuse_prec,(bool), false )
	  (transpose,(bool), false )
	  )
	)
    {
\end{lstlisting}

\noindent The library \lstinline!Boost::Parameters! allows you to enter parameters in the order you want. It supports deduced parameters,  that is to say parameters whose identity can be deduced from their types.



%%% Local Variables:
%%% coding: utf-8
%%% mode: latex
%%% TeX-PDF-mode: t
%%% TeX-parse-self: t
%%% x-symbol-8bits: nil
%%% TeX-auto-regexp-list: TeX-auto-full-regexp-list
%%% TeX-master: "../feelpp-manual"
%%% ispell-local-dictionary: "american"
%%% End:

